Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-03-19 eg6-letters/long-paper/prc-dvcshelium.tex
Reread of long paper part 1

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{lineno}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}

@@

%Title of paper
\title{Measurement of deeply virtual Compton scattering off Helium-4}

@@

\begin{abstract}
Measurements of the beam-spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) are 
reported. A 6 GeV longitudinally polarized electron beam was incident on a 
pressurized $^4$He gaseous target to study the partonic structure of the 
nucleus and the bound nucleons. To ensure the exclusivity of the reactions, 
CLAS was upgraded with a radial time projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance to very forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developpements with three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies can be generalized to the
nucleus and offer a unique opportunity to revisit the quark structure of the nucleus
with an original perspective. This new approach is particularly needed as the quark
structure of the nucleus remains today the subject of numerous
controvercies. Indeed, while much progress has been made in measuring the nuclear
parton distribution functions (PDFs), the observed shape of the PDF ratio, known as
EMC effect, remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the generalized parton distributions (GPDs) can be probed conveniently through
spin assymetries in the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. Indeed, the exclusive
production of a photon limits the possibilities of final state interactions in the nuclear 
medium. Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
is significantly simplified with the reduction to a single GPD intervening in the process. The 
measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
the HERMES collaboration \cite{Airapetian:2009cga} lead to imprecise results. We present here
more recent and detailed measurements from the CLAS collaboration already partially presented
in previous letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the nuclear DVCS CLAS experiment, detail the methods used for the
data analysis and produce the full experimental results for each channel measured.

@@

The theory of GPDs has been already reviewed in details in various 
publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
we summarized here only necessary elements to discuss our experimental results.
we obtain real structure functions 
$F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are the incoming and outgoing quark momenta 
respectively and $t=\Delta^2$ the squared transferred momentum to the target as illustrated in 
Fig. \ref{fig:GPD}.

@@

As mentioned above, DVCS is the main experimental access to GPDs. However, this process does not offer
a full access to the GPDs and we only access them integrated over $x$, in the following form:
\begin{equation}
	\int^1 _{-1} dx F^{q}(x,\xi,t) \left [ {1 \over x - \xi - i \epsilon} 
	                                   \mp {1 \over x + \xi - i \epsilon} \right]. 
\end{equation}
To account for this and simplify equations, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
	\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
	      \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
	\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
quark flavors. A similar situation exists for TCS and DVMP giving only a partial access to the GPDs. 
The double DVCS is a special case and it retains the full
dependence of the GPDs in three independent variables.

Experimentally, another process is indistinguishable from the DVCS. This is the Bethe-Heitler (BH) 
process in which % TODO add BH figure
the final state photon is emitted by the scattering lepton rather than the hadron. In this case the 
photon-hadron interaction is the same as in elastic scattering and therefore such process depends on the
target FFs rather than its GPDs. The DVCS and BH processes are experimentally indistinguishable as they
have identical final states, such that they interfere in the squared photo-production amplitude of the
exclusive photo-production process:
\begin{equation}
	|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms increase significantly the cross section in specific parts of the phase space
and lead to significant charge and spin asymmetries.

Finally, we need to define our kinematics properly. We use the 
conventions from Fig. \ref{fig:PhiAngle}. 
In experiments, we generally use slightly different kinematic variables : 
$-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
$x = {2\xi \over 1+\xi}$.

@@

The reaction measured in the experiment is the coherent electro-production of a photon on helium
$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The 
leading order diagrams
of this reaction are the coherent DVCS and BH processes. The nuclear coherent DVCS is 
represented in Fig. \ref{fig:CohDiag}. As  
the two processes interfere at the amplitude level, which give rise to sizable spin asymmetries.
In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and defined as:  
\begin{equation}
A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
  \label{eq:BSA}
\end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as:        
\begin{eqnarray}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
\label{eq:coh_BSA}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target \cite{Kirchner:2003wt}. %The explicit 
%expressions of these coefficients can be found in Appendix 
%\ref{app:Helium_cross_section}.

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
\caption{Diagram representing the coherent nuclear DVCS.}
\label{fig:CohDiag}
\end{figure}
%TODO fix delta

@@

%Their explicit expressions can be found in Appendix 
%\ref{app:Helium_cross_section}.

@@

An important issue with the use of this theoretical framework is the large mass of the 
helium nuclei. In principle, this could lead to significant target mass corrections...
REF? \cite{Braun:2012bg}

@@

The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
the nucleus ($X$) contain only the missing three nucleons. 
The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
already reviewed many times in the litterature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
Two important differences need to be accounted for however, the different initial state and the addition of 
final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
is in an off-shell state that is not exactly identical to its final state. In the final state, 
interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
target are possible, including possible charge exchange. The latter
leading to contamination from other channels, in particular charge exchange can lead to
a large contribution from such background reaction.

@@

The first measurement of nuclear DVCS has been performed by the HERMES collaboration 
\cite{Airapetian:2009cga}.
This experiment covered an array of nuclear target and looked at the $A$ dependence of the
BSA signal. Thier results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large error bars, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about any nuclear effect. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

@@

An important issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution may not be good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which is 
challenging this assumption and could explain the tension between theory and experiment.

@@

\appendix
\section{Detailed equations}
\label{sec:eq}
 tests

>>>>

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
%\usepackage{amsmath,amssymb}             % AMS Math
%\usepackage[francais]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern,textcomp}
%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
\usepackage{setspace}
\usepackage{microtype}
\usepackage{epigraph}
\usepackage{natbib}
%\usepackage[scaled]{helvet}
%\usepackage[pagebackref,hyperindex=true]{hyperref}
%\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{array}
\usepackage{amsmath}

@@

%Title of paper
\title{Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab}

@@

\begin{abstract}
Measurements of the beam-spin asymmetry in the deeply virtual Compton 
scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) are 
reported. A 6 GeV longitudinally polarized electron beam was incident on a 
pressurized $^4$He gaseous target to study the partonic structure of the 
nucleus and the bound nucleons. To ensure the exclusivity of the reactions, 
CLAS was upgraded with a radial time projection chamber to detect the 
low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
photon detection acceptance at forward angles. Our results confirm the 
theoretically predicted enhancement of the coherent 
($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
observed on the free proton, while the incoherent 
($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
From the coherent data, we were able to extract, in a model-independent way, 
the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}

@@

In the past few decades, the study of the proton structure has made significant progress
thanks to the theoretical and experimental developpements with three dimensional 
structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
parton distributions (GPD) and transverse momentum dependent parton distribution functions (PDF)
can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
of the nucleus with an original perspective~\cite{Dupre:2015jha}. This new approach is 
particularly needed as the quark structure of the nucleus remains today the subject of numerous
controvercies. Indeed, while much progress has been made in measuring the nuclear
PDFs, their shape remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.

In nuclei, the GPDs can be probed conveniently through the measurement of the
spin assymetries generated by the deeply virtual Compton scattering (DVCS) 
process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
production of a photon limits the possibilities of final state interactions in the nuclear 
medium and offers a unique opportunity to make a measurement free of final state interactions 
(FSI). Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
is significantly simplified with the reduction to a single GPD intervening in the process at leading order. The 
measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
the HERMES collaboration \cite{Airapetian:2009cga} lead to controversial conclusions. We present here
in detail the more recent measurements from the CLAS collaboration, which has been already partially presented
in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
the description of the nuclear DVCS CLAS experiment, detail the methods used for the
data analysis and produce the complete experimental results for each channel measured.

@@

The theory of GPDs has been already reviewed in details in various 
publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
we summarized here only necessary elements to discuss our experimental results.
The GPDs are real structure functions $F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are incoming and outgoing quark momenta 
respectively and $t=\Delta^2$ the squared transferred momentum to the target in this exchange of quarks as illustrated in 
Fig. \ref{fig:GPD}.

@@

DVCS is the main experimental access to GPDs. However, this process does not offer
a full access to the GPDs and we only access them integrated over $x$, in the following form:
\begin{equation}
	\int^1 _{-1} dx F^{q}(x,\xi,t) \left [ {1 \over x - \xi - i \epsilon} 
	                                   \mp {1 \over x + \xi - i \epsilon} \right]. 
\end{equation}
To account for this and simplify equations, we define the complex Compton form factors (CFF,
noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
\begin{equation}
	\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
	      \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
\end{equation}
\begin{equation}
	\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
\end{equation} 
These are the quantities directly present in the DVCS cross sections. We note that they are summed over
the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
quark flavors.

Experimentally, another process is indistinguishable from the DVCS, the Bethe-Heitler (BH) 
process in which % TODO add BH figure ?
the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
photon-hadron interaction is the same as in elastic scattering and depends on the
target FFs rather than its GPDs. The DVCS and BH processes are experimentally indistinguishable as they
have identical final states, such that they interfere in the squared amplitude of the
exclusive photo-production process:
\begin{equation}
	|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
\end{equation}
The interference terms increase significantly the cross section in specific parts of the phase space
and lead to significant beam spin asymmetries (BSA), which are the focus of the measurements presented 
here.

Finally, we need to define our kinematics properly. We use the 
conventions from Fig. \ref{fig:PhiAngle} for angles and the experimental kinematic variables
used here are defined as: 
$-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
$x_B = {Q^2 \over 2 M_N \nu}\sim {2\xi \over 1+\xi}$, with $M_N$ the nucleon mass and $\nu$ the
energy transfer to the target $\nu = {E -E^\prime} $.

@@

The first reaction measured in the experiment is the coherent electro-production of a photon on helium
$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The 
leading order diagram of the nuclear coherent DVCS is represented in Fig. \ref{fig:CohDiag}.
In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and defined as:  
\begin{equation}
A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
  \label{eq:BSA}
\end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as \cite{Kirchner:2003wt}:        
\begin{eqnarray}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
\label{eq:coh_BSA}
\end{eqnarray}
where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target. The explicit 
expressions of these coefficients, which have been derived based on the work of 
Kirchner and Müller \cite{Kirchner:2003wt}, can be found in Appendix \ref{app:Helium_cross_section}.

\begin{figure}[tbp!]
\center
\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
\caption{Diagram representing the coherent nuclear DVCS.}
\label{fig:CohDiag}
\end{figure}

@@

@@

An important issue with the use of this theoretical framework is the large mass of the 
helium nuclei. Recent work indicate that the effect of this correction is moderate 
\cite{Braun:2012bg}, however the applicability to such a large mass remains to be
fully explored from the theoretical point of view.

@@

The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
the nucleus ($X$) contain only the missing three nucleons. 
The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
already reviewed many times in the litterature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
Two important differences need to be accounted for however, the different initial state and the addition of 
final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
is in an off-shell state that is not exactly identical to its final state. In the final state, 
interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
target are possible. The latter leading to contamination from other channels, in particular 
charge exchange processes can lead to a large contribution from such background reaction.

@@

The first measurement of nuclear DVCS has been performed by the HERMES 
collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
nuclear targets and looked at the $A$ dependence of the
BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
from large error bars, which makes them consistent with the free proton data and prevents us to
reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
strong effect was expected, leading to a conflict between the HERMES results and theoretical
expectations.

@@

An important issue with the HERMES measurement and how it is obtained from data has been raised in
\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
The main concern is that the DVCS process is not fully detected and the scattered target
is instead reconstructed through a missing mass measurement of the other reaction products. The 
issue with this method is that the detector resolution is not good enough to separate the 
coherent and incoherent channels properly. 
Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
$-t$, respectively. This label is based on the assumption that the very different behavior of the
cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which is 
challenging this assumption and could explain the tension between theory and experiment.

@@

\appendix
\section{Expressions for the BSA of the coherent DVCS}
\label{sec:eq}

 The differential cross section for a longitudinally-polarized electron beam ($\lambda$) and an unpolarized $^4$He target can written as:
\small
\begin{equation}
\frac{d^{5}\sigma_{\lambda}}{dx_{A} dQ^{2} dt d\phi_{e} d\phi} = 
\frac{\alpha^{3}}{16 \pi^{2}} \frac{x_{A} \, y^{2}}{Q^{4} \sqrt{1 + \epsilon ^{2}}} 
\frac{
|\mathcal{T}_{BH}|^{2} + |{\mathcal{T}}_{DVCS}^{\lambda}|^{2} + {\mathcal{I}}_{BH*DVCS}^{\lambda}}{e^{6}}
\label{eq:sigdiff}
\end{equation}
\normalsize
where $y = \frac{p \cdot q}{p \cdot k}$, $\epsilon  =  \frac{2 x_{A} M_{A}}{Q}$ 
and $x_A  =  \frac{Q^2}{2 p \cdot q}$. The different amplitudes can be written 
as \cite{BM_2009}:
\small
\begin{equation}
|\mathcal{T}_{BH}|^{2} =  
\frac{e^{6} (1 + \epsilon^{2})^{-2}}{x^{2}_{A} y^{2} t \mathcal{P}_{1}(\phi) \mathcal{P}_{2}(\phi)} \left[ c_{0}^{BH} + c_{1}^{BH} \cos(\phi) + c_{2}^{BH} \cos(2\phi)\right] 
\label{TTBH}
\end{equation}

\begin{equation}
|\mathcal{T}_{DVCS}|^{2} =  \frac{e^{6}}{y^{2} Q^{2}} \left[ c_{0}^{DVCS} + \sum_{n=1}^{2} \Bigg( c_{n}^{DVCS} \cos(n \phi) + \lambda s_{n}^{DVCS} \sin(n \phi)\Bigg) \right] 
\label{TTDVCS}
\end{equation}

\begin{equation}
\mathcal{I}_{BH*DVCS} =  \frac{\pm e^{6}}{x_A y^{3} t \, \mathcal{P}_{1}(\phi) 
\mathcal{P}_{2}(\phi)} \left[ c_{0}^{I} + \sum_{n=0}^{3} \Bigg( c_{n}^{I} \cos(n \phi) + \lambda s_{n}^{I} \sin(n \phi) \Bigg) \right] 
\label{TTinter} 
\end{equation}
\\
\normalsize
where $\mathcal{P}_{1}(\phi)$ and $\mathcal{P}_{2}(\phi)$ are BH propagators and defined as:
\small
\begin{align}
&\mathcal{P}_{1}(\phi) = \frac{(k - q')^{2}}{Q^{2}} = - \frac{1}{y (1 + \epsilon^{2})} 
\big[ J + 2 K \cos(\phi) \big] \\
&\mathcal{P}_{2}(\phi) = \frac{(k - \Delta)^{2}}{Q^{2}} = 1 + \frac{t}{Q^{2}} + 
\frac{1}{y (1 + \epsilon^{2})} \big[ J + 2 K \cos(\phi) \big]
\end{align}
~~~~~~~~~~~with,
\begin{align}
& J = \bigg( 1 - y - \frac{y \epsilon^{2}}{2} \bigg) \bigg(1 + \frac{t}{Q^{2}} \bigg) - 
(1 - x_{A})(2 - y) \frac{t}{Q^{2}} \\
& K^{2} = - \delta t \, (1 - x_{A}) \bigg( 1 - y - \frac{y^{2} \epsilon^{2}}{4} \bigg) 
\bigg\{ \sqrt{1 + \epsilon^{2}} + \frac{4 x_{A} (1-x_{A}) + \epsilon^{2}}{4 (1 - x_{A})}
\delta t \bigg\} \\
& \delta t = \frac{t - t_{min}}{Q^{2}} = \frac{t}{Q^{2}} + \frac{2(1-x_{A}) \left(1- \sqrt{1 + 
\epsilon^{2}} \right) + \epsilon^{2}}{4 x_{A} (1- x_{A}) + \epsilon^{2}}
\end{align}
\normalsize
where $t_{min}$ represents the kinematic boundary of the process and defined as:
\small
\begin{equation}
t_{min} = Q^2 \frac{2(1-x_A)(1 - \sqrt{1+\epsilon^2}) + \epsilon^2}{4 x_A(1-x_A) + \epsilon^2}
\end{equation}
\normalsize
The Fourier coefficients, in equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}, of a spin-0 target are defined as:
\small
\begin{eqnarray}
c_0^{BH} = & \bigg[ & \left\{ {(2-y)}^2 + y^2{(1+\epsilon^2)}^2 \right\} 
\left\{ \frac{\epsilon^2 Q^2}{t} + 4 (1-x_A) + (4x_A+\epsilon^2) \frac{t}{Q^2} 
\right\} \nonumber \\
& \phantom{\bigg[} & + 2 \epsilon^2 \left\{ 4(1-y)(3+2\epsilon^2) + y^2(2-\epsilon^4) 
\right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
& \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
c_1^{BH} = & \phantom{\bigg[} & -8 (2-y) K \left\{ 2 x_A + \epsilon^2 - 
\frac{\epsilon^2 Q^2}{t} \right\} F_A^2(t)  \\
c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t) 
\end{eqnarray} 
\normalsize
where $F_A(t)$ is the electromagnetic form factor of the $^4$He. At leading twist, the $|\mathcal{T}_{DVCS}|^{2}$ writes as a function of only one CFF according to
\small
\begin{equation}
%c_0^{DVCS} = 2 (2-2y+y^2) \, {\mathcal H}_A {\mathcal H}^{\star}_A 
   c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
   {\mathcal H}_A {\mathcal H}^{\star}_A 
   \label{eq:c0DVCS}
\end{equation}
\normalsize
and the interference amplitude coefficients are written as:
\small
\begin{equation}
s_{1}^{INT} = F_{A}(t) \Im m(\mathcal{H}_{A}) S_{++}(1),
\end{equation}
with
\begin{eqnarray}
   S_{++}(1) &=& \frac{-8K(2-y)y}{1+\epsilon^2} \left( 1 + 
\frac{1-xA+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
\frac{t-t_{min}}{Q^{2}} \right) \label{eq:s1I}
\end{eqnarray}

%c_0^{INT} & = & - 8 (2 - y) \frac{t}{Q^2} F_A \, \Re e \{{\mathcal H}_A\} 
%\label{eq:c0I} \\
% & \times & \left\{ (2-x_A)(1-y) - (1-x_A){(2-y)}^2 \left( 1 - 
% \frac{t_{min}}{Q^2} \right) \right\} \nonumber \\

%c_1^{INT} & = & 8 K (2y-y^2-2) F_A \, \Re e \{{\mathcal H}_A\} \label{eq:c1I}

\begin{eqnarray}
\small
c_0^{INT} &=& F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(0),
\end{eqnarray}
with \begin{eqnarray}  C_{++}(0) &=&
\frac{-4(2-y)(1+\sqrt{1+\epsilon^{2}})}{(1+\epsilon^{2})^2}  \bigg\{ 
   \frac{\widetilde{K}^2}{Q^2}  \frac{(2-y)^2}{\sqrt{1+\epsilon^{2}}} \, \\
   &+& \frac{t}{Q^2}  \left( 1 - y - \frac{\epsilon^2}{4} y^2 \right)  
(2-x_{A}) \left(  1 + \frac{2x_A(2-x_A + \frac{\sqrt{1+\epsilon^{2}}-1}{2} + 
\frac{\epsilon^{2}}{2x_A})\frac{t}{Q^2} + \epsilon^{2}}{(2-x_A) 
(1+\sqrt{1+\epsilon^{2}})}  \right)  \bigg\} \nonumber
 \label{eq:c0I} 
 \end{eqnarray}

\begin{eqnarray}
   c_1^{INT} &=&  F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(1),
\end{eqnarray}
with

   \begin{eqnarray}
   C_{++}(1) &=&
   \frac{-16K(1-y+\frac{\epsilon^{2}}{4}y^2)}{(1+\epsilon^{2})^{5/2}}\bigg\{\left(1+(1-x_A)\frac{\sqrt{1+\epsilon^{2}}-1}{2x_A} 
   + \frac{\epsilon^{2}}{4x_A}\right) 
\frac{x_At}{Q^2}-\frac{3\epsilon^{2}}{4.0} \bigg\} \nonumber \\&-& 4K \left( 
2-2y+y^2+\frac{\epsilon^{2}}{2}y^2\right)\frac{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}{(1+e2)^{5/2}}\bigg\{1-(1-3x_A)\frac{t}{Q^2}\nonumber\\&\,\,\,\,&\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,+\frac{1-\sqrt{1+\epsilon^{2}}+3\epsilon^{2}}{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}} 
\frac{x_A*t}{Q^2}\bigg\} \label{eq:c1I}
\end{eqnarray}

\section{Table of results with information on full kinematics}
\label{sec:fullresults}
 tests
